Spatial modelling of the two-party preferred vote in Australian federal elections: 2001--2016

### 2019-04-21 paper.tex
Remove numbering of subsubsections

\documentclass[times, doublespace]{anzsauth}
\usepackage[]{times}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[left=5cm,top=5cm]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Spatial modelling of the two-party preferred vote in Australian federal elections: 2001--2016},
            pdfauthor={Jeremy Forbes\^{}*, Dianne Cook, Rob J Hyndman},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\pretitle{\begin{center}\Large\bfseries}
\posttitle{\end{center}\vspace{0.5cm}}
\preauthor{\begin{center}\large}
\postauthor{\end{center}\begin{center}\emph{Department of Econometrics \& Business Statistics, Monash University, Australia}\footnotetext{$^*$Corresponding author. Email: \texttt{jeremyforbes1995@gmail.com}}\end{center}}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

Electoral socio-demographics are derived from the Australian Census, and vote counts are obtained from Australian federal elections. Joining these two data sources is problematic as there is an inherent asynchronicity in the two types of events. A Census is conducted by the Australian Bureau of Statistics (ABS) every five years, whereas federal elections, conducted by the Australian Electoral Commission (AEC), usually occur every three years or so. The first problem addressed is that of constructing appropriate Census data for the 2004, 2007, 2010 and 2013 elections --- election years in which a Census does not occur. The predominant approach in previous studies was to join voting outcomes to the nearest Census, without accounting for any temporal differences (see Davis and Stimson 1998; Stimson, McCrea, and Shyy 2006; Liao, Shyy, and Stimson 2009; Stimson and Shyy 2009). Furthermore, electoral boundaries change regularly, so spatial discrepancies also arise when matching with electoral data. To obtain appropriate ``Census-like'' data for these four elections, electoral socio-demographics are constructed using a spatio-temporal imputation that combines areal interpolation (Goodchild, Anselin, and Deichmann 1993) and linear time-interpolation. Collecting and wrangling the raw data, along with the imputation process, are detailed in Section \ref{data}. All data and associated documentation relating to this procedure are available in the \texttt{eechidna} \texttt{R} package (Forbes et al. 2019), providing a resource for future analysis.

Previous work on modelling Australian federal elections has found that aggregate socio-demographics are relatively good predictors of voting outcomes. Forrest et al. (2001) used multiple regression to model the Liberal and Labor primary vote for polling booths in the Farrer electorate in 1998 as a function of Census variables from 1996. Stimson, McCrea, and Shyy (2006), Stimson and Shyy (2009) and Stimson and Shyy (2012) used principal component analysis of polling booths in the 2001, 2004 and 2007 elections respectively, also finding that socio-demographic characteristics of polling booths are linked to their two-party preferred vote. In contrast, Stimson and Shyy (2009) models the polling booth swing vote (change in the two-party preferred vote) in the 2007 election, finding that little of the swing vote can be explained by Census data.

@@

Raw data was sourced online from the AEC and ABS websites in \texttt{.csv} and \texttt{.xlsx} files. The formats of these files differ over the years, making extracting the appropriate information a big task. The functions available in the \texttt{dplyr} (Wickham, François, et al. 2019) and \texttt{readxl} (Wickham, Bryan, et al. 2019) \texttt{R} packages are particularly useful, as they provide fast consistent tools for data manipulation and functions to import \texttt{.xlsx} files (respectively). The 2001 and 2006 Census data are published in a format where the information for each electorate is held in a separate document making it difficult to use the \texttt{dplyr} tools. Instead, cells have to be selected from each individual file to construct the desired variables. All scripts required for the data wrangling process can be found in the github repository for the \texttt{eechidna} \texttt{R} package (Forbes et al. 2019), along with the raw data. The \texttt{eechidna} package makes this study entirely reproducible and provides a resource to help wrangle data for future Censuses and elections, when they become available.

@@

\hypertarget{differences-between-census-and-election-data}{%
\subsubsection{Differences between Census and election data}\label{differences-between-census-and-election-data}}

@@

\hypertarget{spatio-temporal-imputation}{%
\subsubsection{Spatio-temporal imputation}\label{spatio-temporal-imputation}}

@@

To account for spatial differences, the piecewise approximation method in Goodchild, Anselin, and Deichmann (1993) is adopted. Consider a map of source zones \(s = 1,\dots,S\), for which socio-demographic information is available, and a set of target zones \(t = 1,\dots,T\) for which information is to be imputed. This is described in the context of a single election, and a single neighbouring Census.

@@

The spatial error model (Anselin 1988) is chosen because it captures spatial heterogeneity by incorporating a spatially structured random effect vector (LeSage, Kelley Pace, and Pace 2009). In this context, the random effect can be thought of as capturing the unobserved political climate in each electorate, where this climate is correlated with the climate in neighbouring electorates, under the assumption that the climate is independent of electoral socio-demographics.

>>>>

\documentclass[times, doublespace]{anzsauth}
\usepackage[]{times}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Spatial modelling of the two-party preferred vote in Australian federal elections: 2001--2016},
            pdfauthor={Jeremy Forbes\^{}*, Dianne Cook, Rob J Hyndman},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{anzsj}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\pretitle{\begin{center}\Large\bfseries}
\posttitle{\end{center}\vspace{0.5cm}}
\preauthor{\begin{center}\large}
\postauthor{\end{center}\begin{center}\emph{Department of Econometrics \& Business Statistics, Monash University, Australia}\footnotetext{$^*$Corresponding author. Email: \texttt{jeremyforbes1995@gmail.com}}\end{center}}

@@

Electoral socio-demographics are derived from the Australian Census, and vote counts are obtained from Australian federal elections. Joining these two data sources is problematic as there is an inherent asynchronicity in the two types of events. A Census is conducted by the Australian Bureau of Statistics (ABS) every five years, whereas federal elections, conducted by the Australian Electoral Commission (AEC), usually occur every three years or so. The first problem addressed is that of constructing appropriate Census data for the 2004, 2007, 2010 and 2013 elections --- election years in which a Census does not occur. The predominant approach in previous studies was to join voting outcomes to the nearest Census, without accounting for any temporal differences \citep[see][]{DavisStimson98, Stimson06, Liao09, Stimson09}. Furthermore, electoral boundaries change regularly, so spatial discrepancies also arise when matching with electoral data. To obtain appropriate ``Census-like'' data for these four elections, electoral socio-demographics are constructed using a spatio-temporal imputation that combines areal interpolation \citep{Goodchild1993} and linear time-interpolation. Collecting and wrangling the raw data, along with the imputation process, are detailed in Section \ref{data}. All data and associated documentation relating to this procedure are available in the \texttt{eechidna} \texttt{R} package \citep{eechidna}, providing a resource for future analysis.

Previous work on modelling Australian federal elections has found that aggregate socio-demographics are relatively good predictors of voting outcomes. \citet{Forrest01} used multiple regression to model the Liberal and Labor primary vote for polling booths in the Farrer electorate in 1998 as a function of Census variables from 1996. \citet{Stimson06}, \citet{Stimson09} and \citet{Stimson12} used principal component analysis of polling booths in the 2001, 2004 and 2007 elections respectively, also finding that socio-demographic characteristics of polling booths are linked to their two-party preferred vote. In contrast, \citet{Stimson09} models the polling booth swing vote (change in the two-party preferred vote) in the 2007 election, finding that little of the swing vote can be explained by Census data.

@@

Raw data was sourced online from the AEC and ABS websites in \texttt{.csv} and \texttt{.xlsx} files. The formats of these files differ over the years, making extracting the appropriate information a big task. The functions available in the \texttt{dplyr} \citep{dplyr} and \texttt{readxl} \citep{readxl} \texttt{R} packages are particularly useful, as they provide fast consistent tools for data manipulation and functions to import \texttt{.xlsx} files (respectively). The 2001 and 2006 Census data are published in a format where the information for each electorate is held in a separate document making it difficult to use the \texttt{dplyr} tools. Instead, cells have to be selected from each individual file to construct the desired variables. All scripts required for the data wrangling process can be found in the github repository for the \texttt{eechidna} \texttt{R} package \citep{eechidna}, along with the raw data. The \texttt{eechidna} package makes this study entirely reproducible and provides a resource to help wrangle data for future Censuses and elections, when they become available.

@@

\hypertarget{differences-between-census-and-election-data}{%
\subsubsection*{Differences between Census and election data}\label{differences-between-census-and-election-data}}
\addcontentsline{toc}{subsubsection}{Differences between Census and election data}

@@

\hypertarget{spatio-temporal-imputation}{%
\subsubsection*{Spatio-temporal imputation}\label{spatio-temporal-imputation}}
\addcontentsline{toc}{subsubsection}{Spatio-temporal imputation}

@@

To account for spatial differences, the piecewise approximation method in \citet{Goodchild1993} is adopted. Consider a map of source zones \(s = 1,\dots,S\), for which socio-demographic information is available, and a set of target zones \(t = 1,\dots,T\) for which information is to be imputed. This is described in the context of a single election, and a single neighbouring Census.

@@

The spatial error model \citep{Anselin88} is chosen because it captures spatial heterogeneity by incorporating a spatially structured random effect vector \citep{LeSage2009}. In this context, the random effect can be thought of as capturing the unobserved political climate in each electorate, where this climate is correlated with the climate in neighbouring electorates, under the assumption that the climate is independent of electoral socio-demographics.

\begin{table}[!htbp]\vspace*{-0.4cm}\centering    \caption{Estimated spatial error model parameters (standard errors) for each of the six election years.\vspace*{-0.4cm}}    \label{tab:printmodels}  \scriptsize\tabcolsep=0.35cm \begin{tabular}{@{\extracolsep{1pt}}lrrrrrr} \\[-1.8ex]\hline  \hline \\[-1.8ex]  \\[-1.8ex] & \multicolumn{6}{c}{\vspace{-0.4cm}} \\   & 2001 & 2004 & 2007 & 2010 & 2013 & 2016 \\  \hline \\[-1.8ex]  $\rho$ & 0.46\rlap{$^{***}$} & 0.29\rlap{$^{*}$} & 0.24 & 0.19 & 0.27\rlap{$^{*}$} & 0.50\rlap{$^{***}$}\\  & (0.15\rlap{)} & (0.17\rlap{)} & (0.17\rlap{)} & (0.16\rlap{)} & (0.16\rlap{)} & (0.17\rlap{)}\\  AusCitizen & $-$3.13 & $-$2.64 & $-$2.53 & $-$0.08 & $-$3.40 & $-$1.80 \\    & (2.26\rlap{)} & (2.43\rlap{)} & (2.34\rlap{)} & (2.79\rlap{)} & (2.76\rlap{)} & (2.71\rlap{)} \\    BornAsia & 2.22 & $-$0.95 & $-$1.60 & $-$6.83\rlap{$^{**}$} & $-$3.03 & $-$0.55 \\    & (2.18\rlap{)} & (2.44\rlap{)} & (2.19\rlap{)} & (2.73\rlap{)} & (2.71\rlap{)} & (2.17\rlap{)} \\    Born\_MidEast & $-$1.15 & $-$1.59 & $-$2.01\rlap{$^{*}$} & $-$2.03 & $-$0.92 & $-$1.44 \\    & (1.07\rlap{)} & (1.20\rlap{)} & (1.11\rlap{)} & (1.27\rlap{)} & (1.24\rlap{)} & (1.13\rlap{)} \\    BornSEEuro & $-$3.21\rlap{$^{**}$} & $-$4.24\rlap{$^{***}$} & $-$3.61\rlap{$^{***}$} & $-$4.14\rlap{$^{***}$} & $-$3.69\rlap{$^{***}$} & $-$2.72\rlap{$^{***}$} \\    & (1.42\rlap{)} & (1.46\rlap{)} & (1.02\rlap{)} & (1.19\rlap{)} & (1.07\rlap{)} & (0.97\rlap{)} \\    Born\_UK & 0.25 & $-$0.07 & 0.34 & 0.56 & $-$0.09 & $-$1.32 \\    & (1.00\rlap{)} & (0.98\rlap{)} & (0.90\rlap{)} & (1.07\rlap{)} & (1.04\rlap{)} & (1.04\rlap{)} \\    BornElsewhere & $-$5.04 & $-$4.91 & $-$4.13 & 2.35 & $-$5.23 & $-$4.14 \\    & (3.30\rlap{)} & (3.68\rlap{)} & (3.38\rlap{)} & (4.23\rlap{)} & (4.15\rlap{)} & (3.97\rlap{)} \\    Buddhism & $-$0.49 & $-$0.17 & $-$1.37 & $-$0.83 & $-$0.12 & $-$1.60 \\    & (1.39\rlap{)} & (1.61\rlap{)} & (1.61\rlap{)} & (1.80\rlap{)} & (1.68\rlap{)} & (1.56\rlap{)} \\    Christianity & $-$2.48 & $-$1.23 & 0.38 & 0.50 & 2.41 & 1.68 \\    & (1.73\rlap{)} & (1.85\rlap{)} & (1.83\rlap{)} & (1.99\rlap{)} & (1.85\rlap{)} & (1.78\rlap{)} \\    CurrentlyStudying & $-$2.19\rlap{$^{**}$} & $-$0.13 & 2.06\rlap{$^{*}$} & 2.12\rlap{$^{*}$} & 1.15 & $-$0.16 \\    & (0.99\rlap{)} & (1.13\rlap{)} & (1.17\rlap{)} & (1.25\rlap{)} & (1.26\rlap{)} & (1.18\rlap{)} \\    DeFacto & $-$6.44\rlap{$^{***}$} & $-$5.37\rlap{$^{**}$} & $-$6.43\rlap{$^{***}$} & $-$8.07\rlap{$^{***}$} & $-$6.56\rlap{$^{**}$} & $-$8.53\rlap{$^{***}$} \\    & (1.87\rlap{)} & (2.48\rlap{)} & (2.31\rlap{)} & (3.06\rlap{)} & (3.11\rlap{)} & (2.83\rlap{)} \\    DiffAddress & 3.88\rlap{$^{***}$} & 5.06\rlap{$^{***}$} & 4.22\rlap{$^{***}$} & 5.57\rlap{$^{***}$} & 3.53\rlap{$^{*}$} & 5.67\rlap{$^{***}$} \\    & (0.94\rlap{)} & (1.12\rlap{)} & (0.99\rlap{)} & (1.76\rlap{)} & (1.91\rlap{)} & (1.60\rlap{)} \\    Distributive & 1.27 & 2.01\rlap{$^{*}$} & 1.36 & 1.57 & 2.10\rlap{$^{*}$} & 1.20 \\    & (1.12\rlap{)} & (1.21\rlap{)} & (1.13\rlap{)} & (1.34\rlap{)} & (1.27\rlap{)} & (1.21\rlap{)} \\    Education & 1.08 & 0.52 & $-$5.52\rlap{$^{*}$} & $-$4.08 & $-$4.44 & $-$7.07\rlap{$^{**}$} \\    & (2.38\rlap{)} & (3.12\rlap{)} & (3.27\rlap{)} & (3.95\rlap{)} & (3.78\rlap{)} & (3.55\rlap{)} \\    Extractive & 4.83\rlap{$^{***}$} & 5.45\rlap{$^{***}$} & 5.37\rlap{$^{***}$} & 7.31\rlap{$^{***}$} & 6.71\rlap{$^{***}$} & 7.43\rlap{$^{***}$} \\    & (1.48\rlap{)} & (1.42\rlap{)} & (1.36\rlap{)} & (1.56\rlap{)} & (1.47\rlap{)} & (1.39\rlap{)} \\    FamHouseSize & $-$0.16 & 0.87 & $-$2.40 & $-$2.53 & $-$3.26 & $-$2.91 \\    & (2.19\rlap{)} & (2.72\rlap{)} & (2.69\rlap{)} & (3.25\rlap{)} & (3.28\rlap{)} & (2.90\rlap{)} \\    Incomes & 4.36\rlap{$^{**}$} & 5.03\rlap{$^{*}$} & 9.45\rlap{$^{***}$} & 7.09\rlap{$^{**}$} & 7.97\rlap{$^{***}$} & 12.20\rlap{$^{***}$} \\    & (1.77\rlap{)} & (2.66\rlap{)} & (2.75\rlap{)} & (3.25\rlap{)} & (2.92\rlap{)} & (2.75\rlap{)} \\    Indigenous & 2.91\rlap{$^{*}$} & 1.97 & 2.48 & 2.84 & 0.67 & $-$0.05 \\    & (1.68\rlap{)} & (1.95\rlap{)} & (1.75\rlap{)} & (2.16\rlap{)} & (2.14\rlap{)} & (2.00\rlap{)} \\    Islam & $-$0.92 & $-$0.97 & $-$0.54 & $-$2.50 & $-$0.82 & $-$0.95 \\    & (1.22\rlap{)} & (1.36\rlap{)} & (1.27\rlap{)} & (1.52\rlap{)} & (1.42\rlap{)} & (1.34\rlap{)} \\    Judaism & 1.88\rlap{$^{*}$} & 1.78 & 2.66\rlap{$^{***}$} & 1.97\rlap{$^{*}$} & 2.74\rlap{$^{**}$} & 1.65\rlap{$^{*}$} \\    & (1.05\rlap{)} & (1.13\rlap{)} & (1.01\rlap{)} & (1.15\rlap{)} & (1.10\rlap{)} & (1.00\rlap{)} \\    ManagerAdmin & 2.06\rlap{$^{***}$} & 3.32\rlap{$^{***}$} & 6.00\rlap{$^{***}$} & 5.47\rlap{$^{***}$} & 5.04\rlap{$^{***}$} & 5.78\rlap{$^{***}$} \\    & (0.71\rlap{)} & (0.93\rlap{)} & (0.90\rlap{)} & (1.08\rlap{)} & (1.03\rlap{)} & (1.06\rlap{)} \\    Married & 0.44 & 0.11 & $-$1.22 & $-$0.22 & 0.91 & $-$2.34 \\    & (2.31\rlap{)} & (2.96\rlap{)} & (2.83\rlap{)} & (3.15\rlap{)} & (3.03\rlap{)} & (2.81\rlap{)} \\    MedianAge & 2.32\rlap{$^{*}$} & 4.96\rlap{$^{***}$} & 3.66\rlap{$^{**}$} & 4.00\rlap{$^{*}$} & 2.30 & 2.87 \\    & (1.32\rlap{)} & (1.65\rlap{)} & (1.81\rlap{)} & (2.26\rlap{)} & (2.08\rlap{)} & (1.79\rlap{)} \\    NoReligion & $-$1.57 & $-$0.92 & 0.56 & $-$0.30 & 1.02 & 1.31 \\    & (1.59\rlap{)} & (1.71\rlap{)} & (1.73\rlap{)} & (1.92\rlap{)} & (1.94\rlap{)} & (2.04\rlap{)} \\    OneParentHouse & $-$1.73 & $-$0.45 & $-$0.75 & $-$1.46 & $-$0.77 & $-$0.74 \\    & (1.36\rlap{)} & (1.59\rlap{)} & (1.49\rlap{)} & (1.69\rlap{)} & (1.57\rlap{)} & (1.47\rlap{)} \\    OtherLanguage & $-$0.44 & 5.92 & 9.98\rlap{$^{**}$} & 11.24\rlap{$^{**}$} & 9.00\rlap{$^{*}$} & 9.84\rlap{$^{**}$} \\    & (3.22\rlap{)} & (4.16\rlap{)} & (3.91\rlap{)} & (4.76\rlap{)} & (4.66\rlap{)} & (4.44\rlap{)} \\    PropertyOwned & $-$0.46 & $-$0.53 & 0.67 & $-$0.94 & $-$0.48 & 1.41 \\    & (1.37\rlap{)} & (1.50\rlap{)} & (1.43\rlap{)} & (1.76\rlap{)} & (1.67\rlap{)} & (1.50\rlap{)} \\    RentLoanPrice & $-$1.57 & $-$3.32\rlap{$^{*}$} & $-$4.01\rlap{$^{**}$} & $-$0.97 & $-$0.70 & $-$0.89 \\    & (1.49\rlap{)} & (1.76\rlap{)} & (1.67\rlap{)} & (2.07\rlap{)} & (2.07\rlap{)} & (2.16\rlap{)} \\    SocialServ & 2.51\rlap{$^{*}$} & 1.65 & 2.47\rlap{$^{*}$} & 2.53\rlap{$^{*}$} & 2.35\rlap{$^{*}$} & 4.45\rlap{$^{***}$} \\    & (1.33\rlap{)} & (1.41\rlap{)} & (1.29\rlap{)} & (1.47\rlap{)} & (1.32\rlap{)} & (1.19\rlap{)} \\    Transformative & 3.24\rlap{$^{**}$} & 4.73\rlap{$^{***}$} & 4.84\rlap{$^{***}$} & 4.46\rlap{$^{**}$} & 3.56\rlap{$^{**}$} & 4.58\rlap{$^{***}$} \\    & (1.55\rlap{)} & (1.78\rlap{)} & (1.74\rlap{)} & (1.98\rlap{)} & (1.78\rlap{)} & (1.53\rlap{)} \\    Unemployment & $-$2.45\rlap{$^{*}$} & $-$3.07\rlap{$^{*}$} & 0.29 & 0.08 & 1.67 & 2.79\rlap{$^{**}$} \\    & (1.40\rlap{)} & (1.63\rlap{)} & (1.51\rlap{)} & (1.76\rlap{)} & (1.51\rlap{)} & (1.37\rlap{)} \\    Constant & 50.81\rlap{$^{***}$} & 52.60\rlap{$^{***}$} & 47.31\rlap{$^{***}$} & 49.93\rlap{$^{***}$} & 53.51\rlap{$^{***}$} & 50.49\rlap{$^{***}$} \\    & (0.71\rlap{)} & (0.58\rlap{)} & (0.52\rlap{)} & (0.57\rlap{)} & (0.58\rlap{)} & (0.80\rlap{)} \\   \hline \\[-1.8ex]  Observations & 150 & 150 & 150 & 150 & 150 & 150 \\  Residual Standard Error (GLS) & 4.69 & 5.04 & 4.79 & 5.63 & 5.18 & 4.88\\ \hline  \hline \\[-1.8ex]  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ \end{tabular}  \end{table}
